High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-28 paper/main.tex
backing up progress on discussion section

>>>>

We examined fMRI data collected as participants listened to an auditory
recording of a story, scrambled recordings of the story, or underwent a resting
state scan. We found that cognitively richer stimuli evoked more reliable
(i.e., consistent across people) and information rich brain activity patterns.
The brain patterns are also more compressible, in that each individual
component provided more ``signal'' to temporal decoders relative to components
of data from less cognitively rich conditions (Fig.~\ref{fig:inflection}). Over
time (e.g., as the experiment progressed), these phenomena were strengthened.
Specifically, across story segments, data from more cognitively rich conditions
became more informative and compressible, and data from less cognitively rich
conditions became \textit{less} informative and compressible
(Fig.~\ref{fig:inflection-thirds}). We also repeated these analyses separately
for different brain networks. We found that networks traditionally associated
with higher-level cognitive functions tended to provide more informative brain
patterns than networks traditionally associated with lower level cognitive
functions (Fig.~\ref{fig:networks}). Finally, we examined the most dominant
components of the brain activity patterns from each experimental condition. We
used a reverse inference approach~\citep{RubiEtal17} to identify the terms in
the neuroimaging literature most commonly associated with the corresponding
maps. As summarized in Figure~\ref{fig:discussion}, we found that terms
associated with memory and sensory processing were associated with the
strongest components in all three story listening conditions. Terms associated
with sensory integration were associated with the strongest components in the
intact and paragraph-scrambled conditions. Terms associated with sentence
comprehension, emotion, and valence were associated with the strongest
components in the intact condition. Finally, terms associated with the default
mode network were associated with the strongest components in the
word-scrambled and resting state conditions. Taken together, our findings
indicate that the informativeness and compressibility of our brain activity
patterns are task-dependent, and these properties change systematically with
factors like cognitive richness and depth of processing.
